---
title: "DC3_Sensor"
author: "Ivy Chen, Salwa Ouachtouki"
date: "3/19/2021"
output: html_document
---

1. combine two datasets(join)
2. find the highest Readings for each pollutant
look at the monitor, date find the corresponding wind speed and wind direction
3. Map(Sensor+factory)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
library(dplyr)
library(ggplot2)
library(lubridate)
library(readxl)

sensordata <- import("Sensor Data.xlsx")
meteorologicaldata <- import ("Meteorological Data.xlsx")
monitor <- (sensordata$Monitor)

glimpse(sensordata)
class(sensordata$Chemical) 
```
```{r}
monitor_chemical_reading <- sensordata%>%
  count(Monitor, Chemical)
monitor_chemical_reading

linecolors <- c("#129376", "#FC7701", "#188D05", "#F40AF4")
fillcolors <- c("#93F4DE", "#F9A75E", "#C4F3BC", "F3BCF3")

ggplot(data = monitor_chemical_reading, aes(x = Monitor, y = n)) +
  geom_point(aes(shape = Chemical), alpha = 0.5, size = 3) + 
  theme(legend.position = "right") +
  ggtitle("Sensor Data: Total Readings of Each Chemical by Monitor") +
  xlab("Monitor") + ylab("Total Readings") +
  xlim("1", "2", "3","4","5","6","7","8","9") +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) + 
  theme_bw()
```
Here we can see a symmetrical pattern that almost looks like an identical reflection that is being represented by AGOC-3A and Methlosmolene. Applyimonia and Chlorodinine are stagnant throughout all the monitors at 2200 total readings which is an unexpected behavior. From this we can tell that AGOC-3A is the leading chemical across all of the monitors. 

```{r}
chemical_reading <- sensordata %>% 
  group_by(Chemical, Reading) %>% 
  count(Chemical, Reading)
chemical_reading 

chemical_reading.sub1 <- subset(chemical_reading, Reading > .5)
chemical_reading.sub1

ggplot(data = chemical_reading.sub1, aes(x = Chemical, y = Reading)) +
  geom_point(color = "cornflowerblue") +
  scale_y_continuous(breaks = seq(0, 101, by = 1)) +
  ggtitle("Sensor Data: Chemical Reading for Each Chemical") +
  xlab("Chemical") + ylab("Reading") +
  theme_bw() +
  theme(axis.text.y = element_text(size=6))
```

From this we can see that the highest chemical readins were from AGOC-3A and Methylosmolene and the lowest were from Appluimonia and Chlorodinine. This shows that AGOC-3A and Methylosmolene are most likely the responsible chemicals. 

```{r}
sensordata%>%
  count(Monitor)
```
At first, we assume that there might be some abnormal detections among the monitors such as some of them might be intentionally less functioning than the others. However, we discovered that the number of monitor that recorded the pollutants were very similar. All 9 monitors almost work the same. 

```{r}
chemical_reading<-sensordata %>% 
  group_by(Chemical, Reading) %>% 
  summarize(num = n()) %>%
  arrange(desc(num))
```

We can see that the pollutants with the highest reading are AGOC-3A and Methylosmolene. They were highly released in April, August and December.

```{r}
sensor_meta<-sensordata%>%
  inner_join(metedata, by = c("Date Time"="Date"))
```

The highest wind speed, 6.8 m/s, has the wind direction towards 303.5. The second highest wind speed is 6.7m/s, with a directions towards 282.3. The  6.3 304.2. The monitors that corresponds to the top three wind speed we had above, which detected the most reading of the pollutants are 3 and 4. We infer that these two monitors can lead us to find the factory that is responsible of polluting the environment.


```{r}
library(png)
library(grid)
d <- data.frame(x=c(89,90,109,120), y= c(27,21,26,22))
r <- png::readPNG('MapLargeLabels.png')
rg <- grid::rasterGrob(r, width=unit(1,"npc"), height=unit(1,"npc"))
factories<-ggplot(d, aes(x,y)) + 
  annotation_custom(rg) +
  geom_point(colour="red") +
  scale_x_continuous(expand=c(0,0), lim=c(0,150)) +
  scale_y_continuous(expand=c(0,0), lim=c(0,150)) +
  theme_void() +
  theme(aspect.ratio = nrow(r)/ncol(r)) 
factories
```

These are the locations of the four factories on the map.

